Contextual Combinatorial Cascading Bandits

### 2016-02-05 contextual combinatorial cascading bandits.tex
modify

We propose the {\it contextual combinatorial cascading bandits}, an online partial monitoring game where at each time step a learning agent is given a set of context information, then selects a list of items, and observes stochastic outcomes of a prefix in the selected items by some stopping criterion. In online recommendation, the stopping criterion might be the first item a user selects; in network routing, the stopping criterion might be the first edge blocked in a path. 
We consider position discounts in the list order, so that the agent's reward is discounted depending on the position where the stopping criterion is met.
%We formulate this problem in a general contextual combinatorial cascading bandit setting.
We then propose a UCB-type algorithm, C$^3$-UCB, for this problem and prove an $n$-step regret bound $\tilde{O}(\sqrt{n})$ in both the general setting and two special cases. 
Our work generalizes existing studies in several directions, including contextual information,
	position discounts, and a more general cascading bandit model.
Our experiments on synthetic and real datasets demonstrate the advantage of involving contextual information and position discounts.

@@

Multi-armed bandit (MAB) has been extensively studied in statistics and machine learning. 
The problem can be formulated as a system of $K$ base arms whose rewards are random samples from unknown distributions with unknown means.
 The learning agent pulls one arm every time and tries to minimize the cumulative regret, 
which is the difference in cumulative rewards between always pulling the best arm in expectation and
 playing according to the agent's strategy.
The problem of MAB has to deal with the trade-off between exploitation (pulling the best empirical arm) and exploration (trying other arms which are not sufficiently pulled).

@@

Cascading feedback model fits into many real application scenarios.
For example, in online or mobile recommendation, it is a typical practice that an ordered list
	(instead of a single item) is recommended to a user, who
	usually goes over the list based on the recommended order and selects one of her interest to
	click through.
Thus it is reasonable to assume that items before the clicked item is of no interest to the user
	while user's interest to items after the clicked item is unclear.
Another example is in networking routing, where the agent needs to select a routing path that is least
	likely of being blocked.
To determine whether a path is blocked, the agent checks from the source node until meeting a blocked edge. 
The edges before the blocked one are unblocked and the edges after the blocked one are unobserved.
In both of the above applications, we observe the feedbacks of a prefix of items in the chosen ordered list. The bandit problem with such cascading feedback has been studied in \cite{kveton2015cascading,kveton2015combinatorial}. 
In this paper, we generalize their work in several directions to cover more realistic scenarios.

First, we incorporate contextual information into cascading bandits.
In online recommendation, contextual information includes various user and item information, 
	and user behaviors in different contexts are different.
Therefore utilizing contextual information is crucial for personalized recommendation.
In network routing, temporal and spacial contextual information may also be useful to
	determine better routing paths.
Therefore, we incorporate contextual information into the cascading bandit formulation.
Second, cascading bandits studied in \cite{kveton2015cascading,kveton2015combinatorial}
	treats all positions in the cascading list equally, but in applications different positions
	may bring different rewards.
For example, in online recommendation, we usually prefer users to find their interested item
	in the list as early as possible to increase user satisfaction.
In network routing, we may prefer to hit a blocked edge as late as possible.
To model these preferences, we introduce position discounts to the cascading bandit, and
	we show through experiments that incorporating position discounts may significantly
	improve the learning result.
Finally, we generalize the reward functions of \cite{kveton2015cascading,kveton2015combinatorial},
	which are based on disjunctive and conjunctive binary random variables, to more general
	non-linear reward functions satisfying monotonicity and Lipschitz continuity conditions.
This generalization allows us to cover new realistic scenarios not covered in
	\cite{kveton2015cascading,kveton2015combinatorial}, and we give such an example
	in Section~\ref{sec:diss}.

@@

The work of \cite{kveton2015cascading} introduced the cascading model to the multi-armed bandit framework with disjunctive objective, where the set of feasible actions form a uniform matroid, and the reward of an action is $1$ if there is at least one ``good'' item in the list. 
The combinatorial cascading bandits of \cite{kveton2015combinatorial} (referred to as `CombCascade' in Table \ref{table:outline}) generalized the framework, allowing each feasible action to be a subset of ground items under combinatorial constraints. It studied a problem of combinatorial bandits with conjunctive objective, where each feasible action is a chain of items, and reward is $1$ if all items are ``good''. 
Our work generalizes these model and involves both contextual information and position discounts.

The experiments of \cite{kveton2015cascading} found that recommending items in increasing order of their UCBs (meaning the items with lower preference come early) has a better performance than in decreasing order of their UCBs.
This unnatural result is perhaps because the order of items does not affect the reward and thus
	putting low preference items first and high preference items last may result in more feedbacks
	in the cascade.
The position discounts introduced in this paper makes the recommended set in the decreasing order 
	of UCBs, which is more realistic.
The work of \cite{combes2015learning} considered a similar cascading model to that of \cite{kveton2015cascading} with a particular case of contextual information, where a user is recommended with $K$ items selected from a user-related group. Under this particular setting, they considered position discounts.
In our setting, users and items are represented by general feature vectors.

@@

Notice that we do not require the knowledge how $f(A, w)$ is defined. We only assume that the agent has access to an oracle $\cO_{\cS}(w)$ that outputs recommended action $A$. More precisely, an oracle $\cO_{\cS}(w)$ is called an $\alpha$-approximation oracle for some $\alpha \leq 1$, if on given input $w$, the oracle returns an action $A = \cO_{\cS}(w) \in \cS$ satisfying $f(A,w) \geq \alpha f(A^*,w)$ where $A^* = \argmax_{A\in\cS} f(A, w)$. In applications, the oracle $\cO_{\cS}(w)$ is often what the best offline algorithm can achieve. For this reason, in the regret defined next, we compare our online algorithm with what the best offline algorithm can produce, $\alpha f_t^{\ast}$.

@@

\begin{theorem} %main theorem
	\label{thm:main}
	Suppose the expected reward function $f(A, w)$ is a function of expected weights and satisfies the requirements of monotonicity and $B$-Lipschitz continuity. Assume there is an $\alpha$-approximation oracle $\cO_{\cS}$. Then the $\alpha$-regret of our algorithm, C$^3$-UCB, satisfies
	\begin{align}
		R^{\alpha}(n) &\le \frac{2\sqrt{2}B}{p^*} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}  \nonumber \\
		&~~ \cdot \left(R\sqrt{\ln \left[(1 + C_\gamma n/(\lambda d))^d n \right] } + \sqrt{\lambda}\right) + \alpha \sqrt{n}\nonumber \\
		&=O\left(\frac{dBR}{p^*} \sqrt{nK} \ln(C_\gamma n) \right),
	\end{align}
	where $R$ is the sub-Gaussian constant and $C_{\gamma} = \sum_{k=1}^K \gamma_k^2 \leq K$.
\end{theorem}
The regret bound deteriorates as $p^*$ gets smaller. But unfortunately, this reciprocal dependence on $p^*$ is not known to be improvable, even in the special case of disjunctive objective. Indeed, in that case, the bound in Section 2.3 of \cite{kveton2015combinatorial} also has a reciprocal dependence on $p^*$. However, in the special case of conjunctive objective, we will give an improved bound, like \cite{kveton2015combinatorial} does.

\begin{proof}% [of Theorem \ref{thm:main}] %proof outline of main theorem
	The complete proof is in the Appendix. The main idea is to reduce the regret at time $t$, $R^{\alpha}(t, \bA_t)$, to the case that all items in $\bA_t$ have been observed. This reduction is challenging because of contextual information and position discounts $\gamma_k, k \leq K$.

	Assume $\bA_t = (\ba_1^t, \ldots, \ba_{|\bA_t|}^t)$. First by monotonicity and $B$-Lipschitz continuity, we can prove
	$$
		R^{\alpha}(t, \bA_t) \leq 2B \sum_{k=1}^{|\bA_t|} \bbeta_{t-1}(\delta) \gamma_k \| x_{t, \ba_k^t} \|_{\bV_{t-1}}.
	$$
	However, it is hard to estimate an upper bound for $\sum_{t=1}^T \sum_{k=1}^{\abs{\bA_t}} \norm{ x_{t, \ba_k^t} }_{ \bV_{t-1}^{-1} }$ because $\bV_t$ only contains information of observed base arms. Thus we need the following deduction.
	\begin{align*}
    	&\EE[R^{\alpha}(t, \bA_t)|\cH_t] \\
    	\qquad = &\EE \left[ \left. R^{\alpha}(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t = \abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right]\\
    	\qquad \leq & \frac{1}{p^*} \EE \left[ \left. R^{\alpha}(t, \bA_t) \bOne\{\bO_t = \abs{\bA_t}\} \right| \cH_t \right].
    \end{align*}
    Then the cumulative regret is bounded by the discounted sum of the contextual information of observed base arms in $\bV$-norms, which is in turn upper bounded by the following lemma.
    \begin{lemma}
    	\label{lem:XNormSumEst}
    	If $\lambda \geq C_{\gamma}$, then
    	$$
    	\sum_{s=1}^t \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2d\ln \left(1 + C_{\gamma}t/(\lambda d)\right),
    	$$
    \end{lemma}
    The claimed result thus follows.
\end{proof}

@@

In the problem of cascading recommendation, when recommended with an ordered list of items $\bA_t = (\ba_{1}^t,...,\ba_{\abs{\bA_t}}^t)$, the user checks the list in that order. The checking process stops if the user selects one item or has checked all items without selecting anyone. The weight of base arm $a$ at time $t$, $\bw_{t,a}$, is a $\{0,1\}$ value indicating whether the user has selected item $a$ or not. Then the random variable $\bO_t$ satisfies
$$
\bO_t = k, \text{ if } \bw_t(\ba_j^t)=0, \forall\, j < k \text{ and } \bw_t(\ba_k^t) = 1,
$$
or 
$$
\bO_t = \abs{\bA_t}, \text{ if }\bw_t(\ba_j^t) = 0, ~~ \forall\, j \leq \abs{\bA_t}.
$$

If the user selects the $k$-th item, then the learning agent receives reward $\gamma_k \in [0,1]$. Usually the importance of the positions is decreasing: the first position is the most important. Based on this, we assume that
$$
1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0.
$$
If the user does not select any item, the agent gets no reward. At the end of time $t$, the learning agent observes $\bO_t, \bw_t(\ba_k^t), k \leq \bO_t$ and receives a reward
$\br_t = \bw_t(\ba_{\bO_t}^t) \gamma_{\bO_t}$. It is not hard to see that $\br_t = \bigvee_{k=1}^{\abs{\bA_t}} \gamma_k \bw_t(\ba_k^t)$ is the disjunctive of discounted weights,
where we use the notation that $\bigvee_{k=1}^n a_k = \max_{1 \leq k \leq n} a_k$. Notice that the order of $\bA_t$ affects both the feedback and the reward.

Now let us introduce a function $f: \cS \times [0,1]^E \to [0,1]$ on $A = (a_1,...,a_{\abs{A}}) \in \cS, w = (w(1),...,w(L))$ by
\begin{equation}
\label{eq:OrRewardFunc}
f(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_{k} \prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k). 
\end{equation}
It is easily verified that $\br_t = f(\bA_t, \bw_t)$ and that $\EE[\br_t] = f(\bA_t, \theta_{\ast}^{\top}x_t) = f(\bA_t, w_t)$. So $f$ is the expected reward function and also a function of expected weights. It can be proved that $f$ satisfies the properties of monotonicity and $1$-Lipschitz continuity. (All verifications are left in the Appendix.) 
%Notice that in this setting, given weights $w$, there is an oracle $\cO_{\cS}(w)$ that outputs the best action, which is the $K$ items with largest $w_i$ listed in decreasing order. So $\alpha = 1$ and we write $R(n)$ instead of $R^{\alpha}(n)$. 
We have the following corollary.
\begin{corollary}
	\label{cor:or}
	In the problem of cascading recommendation, the expected reward function is defined in Eq.~\eqref{eq:OrRewardFunc}, where $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0$. Then the $\alpha$-regret of our algorithm, C$^3$-UCB, satisfies
	\begin{align}
		R^{\alpha}(n) &\le \frac{2\sqrt{2}}{p^*} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}  \nonumber \\
		&~~ \cdot \left(\sqrt{d\ln[(1 + C_\gamma n/(\lambda d))^d n]} + \sqrt{\lambda}\right) + \alpha \sqrt{n}\nonumber \\
		&=O\left(\frac{d}{p^*} \sqrt{nK} \ln (C_\gamma n) \right).
	\end{align}
\end{corollary}

@@

The above formulation is on the disjunctive objective, that is, at each time step the user stops once she selects one item or has checked all recommended items. Similarly, we could also consider the case of conjunctive objective. In this case, we derive a slightly better result.

The Bernoulli random variable $\bw_{t}(a) \in \{0,1\}$ indicates the weight of item $a$ at time $t$ satisfying Eq. \eqref{eq:expectation}. The learning agent observes the first position $k$ in the given action $\bA_t = (\ba_1^t, \ldots, \ba_{|\bA_t|}^t)$ with $w_t(\ba_k^t)=0$. We also consider partial rewards: if the $k$-th item is the first item with weight $0$, then the learning agent receives reward $1-\gamma_k$; if all items have weight $1$, the learning agent receives reward $1$.

The more items reveals, the more reward the agent should receive. This can be used to model scenarios such as online surveys, where questions are adaptively given, and the more questions observed, the more helpful to the survey conductor. Based on this, we assume that
$$
1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0.
$$
At the end of time $t$, the learning agent observes $\bO_{t}, \bw_t(\ba_k^t), k \leq \bO_{t}$ and receives reward $\br_{t}$:
\begin{align*}
	\br_{t} %&= \begin{cases}
		%1 - \gamma_{\bO_{t}}  &\text{if } \bw_t(\ba_{\bO_{t}}^t) = 0,\\
		%1 &\text{if } \bw_t(\ba_{\bO_{t}}^t) = 1.
	%\end{cases}\\
	&=\begin{cases}
		1-\gamma_{k}  &\text{if } \bw_t(\ba_{i}^t) = 1, \forall i < k, \text{and } \bw_t(\ba_{k}^t) = 0,\\
		1 &\text{if } \bw_t(\ba_{i}^t) = 1, \forall i\leq \abs{\bA_t}.
	\end{cases}
\end{align*}

If we define a function $f : \cS \times [0,1]^E \to [0,1]$ on $A = (a_1, \ldots, a_{\abs{A}}) \in \cS \text{ and } w = (w(1), \ldots, w(L))$ by
\begin{equation}
	\label{eq:AndRewardFunc}
	f(A,w) = \sum_{k = 1}^{\abs{A}} (1 - \gamma_k) \prod_{i = 1}^{k - 1} w(a_i)(1 - w(a_k)) + \prod_{i=1}^{\abs{A}}w(a_i),
\end{equation}
then it is not hard to verify that $\br_{t} = f(\bA_t, \bw_t)$ and $\EE[\br_{t}] = f(\bA_t, w_t) = f(\bA_t, \theta_{\ast}^{\top}x_t)$. Next is our result for the conjunctive objective with a slightly improved bound than Theorem \ref{thm:main}.

\begin{theorem} %main theorem
	\label{thm:and}
	Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_{K} \geq 1 - \frac{\alpha}{4} f^{\ast}$, where $f^* = \min_{t} f_t^{\ast}$ with $f_t^{\ast} = \max_{A \in \cS} f(A, w_t)$. Then the $\alpha$-regret of our algorithm, C$^3$-UCB, for the conjunctive objective satisfies
	\begin{align}
		R^{\alpha}(n) \le& \frac{\sqrt{128}}{\alpha f^{\ast}} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))} \nonumber \\
		&~~ \cdot \left(\sqrt{d\ln[(1 + C_\gamma n/(\lambda d)^d n] } + \sqrt{\lambda}\right) + \alpha \sqrt{n} \nonumber \\
		=&O\left(\frac{d}{\alpha f^{\ast}}\sqrt{nK} \ln(C_{\gamma} n) \right).
	\end{align}
\end{theorem}
\begin{proof}
	(sketch) First, we prove the expected reward function satisfies the properties of monotonicity and Lipschitz continuity. And then we use the following lemma to replace $\bA_t$ with a prefix of $\bA_t$.
	\begin{lemma}
		\CLemmaPrefixExi
	\end{lemma}

@@

Our algorithm also applies to the setting of \cite{chen2013combinatorial} by allowing context information. Note the probability $p^{\ast}$ in our results should be the probability that all base arms in $\tilde{S}$ (in their notations) will be triggered.

>>>>

We propose the {\it contextual combinatorial cascading bandits}, an online partial monitoring game where at each time step a learning agent is given a set of context information, then selects a list of items, and observes stochastic outcomes of a prefix in the selected items by some stopping criterion. In online recommendation, the stopping criterion might be the first item a user selects; in network routing, the stopping criterion might be the first edge blocked in a path. 
We consider position discounts in the list order, so that the agent's reward is discounted depending on the position where the stopping criterion is met.
%We formulate this problem in a general contextual combinatorial cascading bandit setting.
We then propose a UCB-type algorithm, C$^3$-UCB, for this problem and prove an $n$-step regret bound $\tilde{O}(\sqrt{n})$ in both the general setting and give finer analysis for two special cases. 
Our work generalizes existing studies in several directions, including contextual information,
	position discounts, and a more general cascading bandit model.
Our experiments on synthetic and real datasets demonstrate the advantage of involving contextual information and position discounts.

@@

Multi-armed bandit (MAB) has been extensively studied in statistics and machine learning. 
The problem is usually formulated as a system of $K$ base arms whose rewards are random samples from unknown distributions with unknown means.
 The learning agent pulls one arm every time and tries to minimize the cumulative regret, 
which is the difference in cumulative rewards between always pulling the best arm in expectation and
 playing according to the agent's strategy.
The problem of MAB has to deal with the trade-off between exploitation (pulling the best empirical arm) and exploration (trying other arms which are not sufficiently pulled).

@@

Cascading feedback model fits into many real application scenarios.
For example, in online or mobile recommendation, it is a typical practice that an ordered list
	(instead of a single item) is recommended to a user, who
	usually goes over the list based on the recommended order and selects one of her interest to
	click through.
Thus it is reasonable to assume that items before the clicked item is of no interest to the user
	while user's interest to items after the clicked item is unclear.
Another example is in networking routing, where the agent needs to select a routing path that is least
	likely of being blocked.
To determine whether a path is blocked, the agent checks from the source node until meeting a blocked edge. 
The edges before the blocked one are unblocked and the edges after the blocked one are unobserved.
In both of the above applications, we observe the feedbacks of a prefix of items in the chosen ordered list. The bandit problem with such cascading feedback has been studied in recent papers \cite{kveton2015cascading,kveton2015combinatorial}. 
In this paper, we generalize their work in several directions to cover more realistic scenarios.

First, we incorporate contextual information into cascading bandits.
In online recommendation, contextual information includes various user and item information, 
	and user behaviors in different contexts are different.
Therefore utilizing contextual information is crucial for personalized recommendation.
In network routing, temporal and spacial contextual information may also be useful to
	determine better routing paths.
Therefore, we incorporate contextual information into the cascading bandit formulation.
Second, cascading bandits studied in \cite{kveton2015cascading,kveton2015combinatorial}
	treats all positions in the cascading list equally, but in applications different positions
	may bring different rewards.
For example, in online recommendation, we usually prefer users to find their interested item
	in the list as early as possible to increase user satisfaction.
In network routing, we may prefer to hit a blocked edge as late as possible.
To model these preferences, we introduce position discounts to the cascading bandit, and
	we show through experiments that incorporating position discounts may significantly
	improve the learning result.
Finally, we generalize the reward functions of \cite{kveton2015cascading,kveton2015combinatorial},
	which are based on disjunctive and conjunctive binary random variables, to more general
	non-linear reward functions satisfying monotonicity and Lipschitz continuity conditions.
This generalization allows us to cover new realistic scenarios not covered in
	\cite{kveton2015cascading,kveton2015combinatorial}, as exhibited in Section~\ref{sec:diss}.

@@

The work of \cite{kveton2015cascading} introduced the cascading model to the multi-armed bandit framework with disjunctive objective, where the set of feasible actions form a uniform matroid, and the reward of an action is $1$ if there is at least one ``good'' item in the list. 
The combinatorial cascading bandits of \cite{kveton2015combinatorial} (referred to as `CombCascade' in Table \ref{table:outline}) generalized the framework, allowing each feasible action to be a subset of ground items under combinatorial constraints. It studied a problem of combinatorial bandits with conjunctive objective, where each feasible action is a chain of items, and reward is $1$ if all items are ``good''. 
Our work generalizes these models and involves both contextual information and position discounts.

The experiments of \cite{kveton2015cascading} found that recommending items in increasing order of their UCBs (meaning the items with lower preference come early) has a better performance than in decreasing order of their UCBs.
This unnatural result is perhaps because the order of items does not affect the reward and thus
	putting low preference items first and high preference items in the back may result in more feedbacks
	in the cascade.
The position discounts introduced in this paper makes the recommended set in the decreasing order 
	of UCBs, which is more realistic.
The work of \cite{combes2015learning} considered a similar cascading model to that of \cite{kveton2015cascading} with a particular case of contextual information, where a user is recommended with $K$ items selected from a user-related group. Under this particular setting, they considered position discounts.
In our setting, users and items are represented by general feature vectors.

@@

Notice that we do not require the knowledge how $f(A, w)$ is defined. We only assume that the agent has access to an oracle $\cO_{\cS}(w)$ that outputs recommended action $A$. More precisely, an oracle $\cO_{\cS}(w)$ is called an $\alpha$-approximation oracle for some $\alpha \leq 1$, if on given input $w$, the oracle returns an action $A = \cO_{\cS}(w) \in \cS$ satisfying $f(A,w) \geq \alpha f(A^*,w)$ where $A^* = \argmax_{A\in\cS} f(A, w)$. In applications, the oracle $\cO_{\cS}(w)$ is often what the best offline algorithm can achieve. For this reason, in the regret defined next, we compare our online algorithm with what the best offline algorithm can produce, i.e. $\alpha f_t^{\ast}$.

@@

\begin{theorem} %main theorem
	\label{thm:main}
	Suppose the expected reward function $f(A, w)$ is a function of expected weights and satisfies the requirements of monotonicity and $B$-Lipschitz continuity. Then the $\alpha$-regret of our algorithm, C$^3$-UCB, satisfies
	\begin{align}
		R^{\alpha}(n) &\le \frac{2\sqrt{2}B}{p^*} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}  \nonumber \\
		&~~ \cdot \left(R\sqrt{\ln \left[(1 + C_\gamma n/(\lambda d))^d n \right] } + \sqrt{\lambda}\right) + \alpha \sqrt{n}\nonumber \\
		&=O\left(\frac{dBR}{p^*} \sqrt{nK} \ln(C_\gamma n) \right),
	\end{align}
	where $R$ is the sub-Gaussian constant and $C_{\gamma} = \sum_{k=1}^K \gamma_k^2 \leq K$.
\end{theorem}
The regret bound deteriorates as $p^*$ gets smaller. But unfortunately, this reciprocal dependence on $p^*$ is not known to be improvable, even in the special case of disjunctive objective. Indeed, in that case, the bound in Section 2.3 of \cite{kveton2015combinatorial} also has a reciprocal dependence on $p^*$. However, in the special case of conjunctive objective, we will give an improved bound.

\begin{proof}% [of Theorem \ref{thm:main}] %proof outline of main theorem
	(sketch) %The main idea is to reduce the regret at time $t$, $R^{\alpha}(t, \bA_t)$, to the case that all items in $\bA_t$ have been observed. This reduction is challenging because of contextual information and position discounts $\gamma_k, k \leq K$. 
	Assume $\bA_t = (\ba_1^t, \ldots, \ba_{|\bA_t|}^t)$. We first employ the monotonicity and $B$-Lipschitz continuity of $f$ to upper bound regret as follows.
	\begin{equation}
		\label{eq:regretDeduction}
		R^{\alpha}(t, \bA_t) \leq 2B \sum_{k=1}^{|\bA_t|} \bbeta_{t-1}(\delta) \gamma_k \| x_{t, \ba_k^t} \|_{\bV_{t-1}^{-1}}.
	\end{equation}
	As $\bV_t$ contains only information of observed base arms, our UCB-type algorithm guarantees the sum of the first $\bO_t$ items in the right of Ineq. \ref{eq:regretDeduction} to be small, with the leftover sum (from $\bO_t + 1$ to $|\bA_t|$) out of control. We cope with this by a reduction to the case that $\bO_t = |\bA_t|$.
	%However, it is hard to estimate an upper bound for $\sum_{t=1}^T \sum_{k=1}^{\abs{\bA_t}} \norm{ x_{t, \ba_k^t} }_{ \bV_{t-1}^{-1} }$ because $\bV_t$ only contains information of observed base arms. Thus we need the following deduction.
	\begin{align}
    	&\EE[R^{\alpha}(t, \bA_t)|\cH_t] \nonumber\\
    	\qquad = &\EE \left[ \left. R^{\alpha}(t, \bA_t) \EE \left[ \left. \frac{1}{p_{t, \bA_t}} \bOne\{\bO_t = \abs{\bA_t}\} \right| \bA_t \right]  \right| \cH_t \right]\nonumber\\
    	\qquad \leq & \frac{1}{p^*} \EE \left[ \left. R^{\alpha}(t, \bA_t) \bOne\{\bO_t = \abs{\bA_t}\} \right| \cH_t \right]. \label{eq:ot=at}.
    \end{align}
    Combining \ref{eq:regretDeduction} and \ref{eq:ot=at} gives an upper bound of $R^{\alpha}(n)$ in terms of $\sum_{t=1}^n \sum_{k=1}^{\abs{\bO_t}} \gamma_k\norm{ x_{t, \ba_k^t} }_{ \bV_{t-1}^{-1} }$. The next Lemma upper bounds the sum of norms squared.
    %the cumulative regret is bounded by the discounted sum of the contextual information of observed base arms in $\bV$-norms, which is in turn upper bounded by the following lemma.
    \begin{lemma}
    	\label{lem:XNormSumEst}
    	If $\lambda \geq C_{\gamma}$, then for any time $t$,
    	$$
    	\sum_{s=1}^t \sum_{k=1}^{\bO_s} \norm{\gamma_k x_{s,\ba_{k}^s}}_{\bV_{s-1}^{-1}}^2 \leq 2d\ln \left(1 + C_{\gamma}t/(\lambda d)\right).
    	$$
    \end{lemma}
    The claimed result thus follows. See the Appendix for a complete proof.
\end{proof}

@@

In the problem of cascading recommendation, when recommended with an ordered list of items $\bA_t = (\ba_{1}^t,...,\ba_{\abs{\bA_t}}^t)$, the user checks the list in that order. The checking process stops if the user selects one item or has checked all items without selecting anyone. The weight of each base arm $a$ at time $t$, $\bw_{t}(a)$, is a $\{0,1\}$ value indicating whether the user has selected item $a$ or not. Then the random variable $\bO_t$ satisfies
$$
\bO_t = \begin{cases}
k, &\text{ if } \bw_t(\ba_j^t)=0, \forall\, j < k \text{ and } \bw_t(\ba_k^t) = 1,\\
\abs{\bA_t}, &\text{ if }\bw_t(\ba_j^t) = 0, ~~ \forall\, j \leq \abs{\bA_t}.
\end{cases}
$$

If the user selects the $k$-th item, then the learning agent receives a reward $\gamma_k \in [0,1]$. Usually $\{\gamma_k\}$ are decreasing with $k$:
$$
1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0.
$$
If the user does not select any item, the agent gets no reward. At the end of time step $t$, the learning agent observes $\bO_t, \bw_t(\ba_k^t), k \leq \bO_t$ and receives a reward
$\br_t = \bw_t(\ba_{\bO_t}^t) \gamma_{\bO_t}$. It is not hard to see that $\br_t = \bigvee_{k=1}^{\abs{\bA_t}} \gamma_k \bw_t(\ba_k^t)$ is the disjunctive of discounted weights,
where we use the notation that $\bigvee_{k=1}^n a_k = \max_{1 \leq k \leq n} a_k$. Notice that the order of $\bA_t$ affects both the feedback and the reward.

Now let us define a function $f: \cS \times [0,1]^E \to [0,1]$ on $A = (a_1,...,a_{\abs{A}}) \in \cS, w = (w(1),...,w(L))$ by
\begin{equation}
\label{eq:OrRewardFunc}
f(A,w) = \sum_{k = 1}^{\abs{A}} \gamma_{k} \prod_{i=1}^{k-1} (1 - w(a_i)) w(a_k). 
\end{equation}
It is easily verified that $\br_t = f(\bA_t, \bw_t)$ and that $\EE[\br_t] = f(\bA_t, \theta_{\ast}^{\top}x_t) = f(\bA_t, w_t)$. So $f$ is the expected reward function and also a function of expected weights. It can be proved that $f$ satisfies the properties of monotonicity and $1$-Lipschitz continuity. (All verifications are left in the Appendix.) 
%Notice that in this setting, given weights $w$, there is an oracle $\cO_{\cS}(w)$ that outputs the best action, which is the $K$ items with largest $w_i$ listed in decreasing order. So $\alpha = 1$ and we write $R(n)$ instead of $R^{\alpha}(n)$. 
We thus have the following corollary.
\begin{corollary}
	\label{cor:or}
	In the problem of cascading recommendation, the expected reward function is defined in Eq.~\eqref{eq:OrRewardFunc}, where $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0$. Then the $\alpha$-regret of our algorithm, C$^3$-UCB, satisfies
	\begin{align}
		R^{\alpha}(n) &\le \frac{2\sqrt{2}}{p^*} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))}  \nonumber \\
		&~~ \cdot \left(\sqrt{d\ln[(1 + C_\gamma n/(\lambda d))^d n]} + \sqrt{\lambda}\right) + \alpha \sqrt{n}\nonumber \\
		&=O\left(\frac{d}{p^*} \sqrt{nK} \ln (C_\gamma n) \right).
	\end{align}
\end{corollary}

@@

The above formulation is on the disjunctive objective, for which the user stops once she finds a ``good'' item. Similarly, we could also consider the case of conjunctive objective, for which the user stops once she finds a ``bad'' item. In this case, we derive a better result.

The Bernoulli random variable $\bw_{t}(a) \in \{0,1\}$ indicates the weight of item $a$ at time $t$ satisfying Eq. \eqref{eq:expectation}. The learning agent observes the first position $k$ in the given action $\bA_t = (\ba_1^t, \ldots, \ba_{|\bA_t|}^t)$ with $\bw_t(\ba_k^t)=0$. We also consider partial rewards: if the $k$-th item is the first item with weight $0$, then the learning agent receives reward $1-\gamma_k$; if all items have weight $1$, the learning agent receives reward $1$.

The more items reveals, the more reward the agent should receive. This can be used to model scenarios such as online surveys, where questions are adaptively given, and the more questions are observed, the more helpful it is to the survey conductor. Based on this, we assume that
$$
1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_K \geq 0.
$$
At the end of time step $t$, the learning agent observes $\bO_{t}, \bw_t(\ba_k^t), \forall k \leq \bO_{t}$ and receives a reward $\br_{t}$:
\begin{align*}
	\br_{t} %&= \begin{cases}
		%1 - \gamma_{\bO_{t}}  &\text{if } \bw_t(\ba_{\bO_{t}}^t) = 0,\\
		%1 &\text{if } \bw_t(\ba_{\bO_{t}}^t) = 1.
	%\end{cases}\\
	&=\begin{cases}
		1-\gamma_{k}  &\text{if } \bw_t(\ba_{i}^t) = 1, \forall i < k, \text{and } \bw_t(\ba_{k}^t) = 0,\\
		1 &\text{if } \bw_t(\ba_{i}^t) = 1, \forall i\leq \abs{\bA_t}.
	\end{cases}
\end{align*}

If we define a function $f : \cS \times [0,1]^E \to [0,1]$ on $A = (a_1, \ldots, a_{\abs{A}}) \in \cS \text{ and } w = (w(1), \ldots, w(L))$ by
\begin{equation}
	\label{eq:AndRewardFunc}
	f(A,w) = \sum_{k = 1}^{\abs{A}} (1 - \gamma_k) \prod_{i = 1}^{k - 1} w(a_i)(1 - w(a_k)) + \prod_{i=1}^{\abs{A}}w(a_i),
\end{equation}
then it is not hard to verify that $\br_{t} = f(\bA_t, \bw_t)$ and $\EE[\br_{t}] = f(\bA_t, w_t) = f(\bA_t, \theta_{\ast}^{\top}x_t)$. Next is our result for the conjunctive objective with an improved bound than Theorem \ref{thm:main}, with $p^{\ast}$ improved by $\alpha f^{\ast}$. In network routing problem, the $p^{\ast}$ is related with the bad paths, which can make the probability of observing the whole path very small, and $f^{\ast}$ is related with good paths, which makes $f^{\ast}$ usually large.

\begin{theorem} %main theorem
	\label{thm:and}
	Suppose $1 = \gamma_1 \geq \gamma_2 \geq \cdots \geq \gamma_{K} \geq 1 - \frac{\alpha}{4} f^{\ast}$, where $f^* = \min_{t} f_t^{\ast}$ with $f_t^{\ast} = \max_{A \in \cS} f(A, w_t)$. Then the $\alpha$-regret of our algorithm, C$^3$-UCB, for the conjunctive objective satisfies
	\begin{align}
		R^{\alpha}(n) \le& \frac{\sqrt{128}}{\alpha f^{\ast}} \sqrt{nKd\ln(1 + C_\gamma n/(\lambda d))} \nonumber \\
		&~~ \cdot \left(\sqrt{d\ln[(1 + C_\gamma n/(\lambda d)^d n] } + \sqrt{\lambda}\right) + \alpha \sqrt{n} \nonumber \\
		=&O\left(\frac{d}{\alpha f^{\ast}}\sqrt{nK} \ln(C_{\gamma} n) \right).
	\end{align}
\end{theorem}
\begin{proof}
	(sketch) First, we prove the expected reward function satisfies the properties of monotonicity and Lipschitz continuity. Then we use the following lemma to replace $\bA_t$ with a prefix of $\bA_t$.
	\begin{lemma}
		\CLemmaPrefixExi
	\end{lemma}

@@

Our algorithm also applies to the setting of \cite{chen2013combinatorial} by allowing context information. Note the probability $p^{\ast}$ in our results should be the probability that all base arms in $\tilde{S}$ (in their notation) will be triggered.
